---
title: "8 - Exploratory analysis"
execute: 
  warning: false
---


## Work through the tutorial  [Exploring numerical data](https://openintro.shinyapps.io/ims-02-explore-02/) before attempting the lab


## Load libraries and data

```{r}
library(tidyverse)
library(scales)
theme_set(theme_minimal())
```

## Read the data in 

```{r}
cars <- read_csv('https://bus320-quarto.netlify.app/data/cars.csv')
```

## 1. Use `glimpse` to examine the `cars` dataset

```{r}

```

## 2. scatterplot 


- Create a scatterplot of `msrp` on the x-axis and `weight` on the y-axis
  
- Format `msrp` in thousands of dollar 

- Format the `weight` in comma format with suffix "lbs"  (hint: use `labels = comma_format(suffix = "lbs")`) 

- Add main title: "Scatter plot of `msrp` and `weight`"

- Add x-axis title: "Manufacturer suggested retail price"

- Add y-axis title: "Vehicle weight"

```{r}

```

## 3 Dotplot with median

- Create a dotplot of `msrp`
  
- Add a line for the median with a color other than black

- Format `msrp` in thousands of dollar 

- Eliminate the y-axis: `scale_y_continuous(labels = NULL)`

- Add main title: "Dotplot  of `msrp` with median"

- Add x-axis title: "Manufacturer suggested retail price"

- Set y-axis title to NULL

```{r}

```

## 4 Histogram with mean

- Create a histogram of `msrp`
  
- Add a line for the mean with a color other than black

- Format `msrp` in thousands of dollar 

- Eliminate the y-axis:`scale_y_continuous(labels = NULL)`

- Add main title: "Histogram  of `msrp` with mean"

- Add x-axis title: "Manufacturer suggested retail price"

- Set y-axis title to NULL

```{r}

```

## 5 Density plot with median

- Create a density plot of `msrp`
  
- Add a line for the median with a color other than black

- Format `msrp` in thousands of dollar 

- Eliminate the y-axis: `scale_y_continuous(labels = NULL)`

- Add main title: "Density  of `msrp` with median"

- Add x-axis title: "Manufacturer suggested retail price"

- Set y-axis title to NULL

```{r}

```

## 6 Boxplot

- Create a boxplot of `msrp`
  
- Format `msrp` in thousands of dollar 

- Eliminate the y-axis:  `scale_y_continuous(labels = NULL)`

- Add main title: "Boxplot of `msrp`"

- Add x-axis title: "Manufacturer suggested retail price"

- Set y-axis title to NULL

```{r}

```

