---
title: "9 - Visualization"
execute: 
  warning: false
---



## Load libraries and data

```{r}
library(tidyverse)
library(scales)
library(ggcharts) # for bar_chart and lollipop_chart
theme_set(theme_ggcharts()) #set theme of all plots 
```

## Read the data in 

```{r}
drug_cos<-  read_csv("https://bus320-quarto.netlify.app/data/drug_cos.csv")
```

## 1. Glimpse the data

- Use `glimpse` to examine the `drug_cos` dataset

```{r}

```

## 2. Observations for each `name` 

- Use `count` to find the number of observations for each company `name`

```{r}

```

## 3. Observations for each `year`  

- Use `count` to find the number of observations for each `year` 

```{r}

```


## 4. Bar chart of 2016 net margin


- Use `bar_chart` from the `ggcharts` package create a bar chart of the 2016 `netmargin` 

- Format the y-axis to show the percentage sign

- Eliminate the x- the y-axes labels

- Title the chart "2016 Net Margin for Drug Companies"

```{r}

```

## 5. Bar chart of 2015 roe with highlight


- Use `bar_chart` from the `ggcharts` package create a bar chart of the 5 companies with the highest `roe` in 2015 

- Format the y-axis to show the percentage sign

- Eliminate the x- the y-axes labels

- Title the chart: "Top 5 Drug Companies by 2015 ROE" 

- Highlight the bar of the company with the highest `roe` in your chart

```{r}

```

## 6. Lollipop chart of 2015 `ros` with highlight

- Create a `lollipop_chart` of the top 10 companies by 2015 return on sales (`ros`)

- Format the y-axis to show the percentage sign

- Eliminate the x- the y-axes labels

- Title the chart: "Top 10 Drug Companies by 2015 ROS" 

- Highlight the bar of the company with the second highest `ros` in your chart

```{r}

```

## 7. 4 Bar charts for 3 companies for years (2015-2018)

- Use `bar_chart` from the `ggcharts` package create a separate  a bar chart of the `netmargin` for "Pfizer Inc", "Merck & Co Inc" and"Johnson & Johnson"

- Format the y-axis to show the percentage sign

- Eliminate the x- the y-axes labels

- Title the chart: "Net margin for Pfizer, Merck and Johnson & Johnson" 

- See example [here](https://thomas-neitmann.github.io/ggcharts/index.html#bar_chart)
  - Hint: use `filter` to subset the data for the 3 companies and 4 years
  - Hint: use the `facet` argument in the `bar_chart` function to create 4 charts

```{r}

```
