---
title: "7 - Exploratory analysis"
execute: 
  warning: false
---


## Work through the tutorial  [Exploring categorical data](https://openintro.shinyapps.io/ims-02-explore-01/) before attempting the lab


## Load libraries and data

```{r}
library(tidyverse)
library(ggmosaic) 
```

## Read the data in 

```{r}
comics  <- read_csv('https://bus320-quarto.netlify.app/data/comics.csv')
```

## 1. Use `glimpse` to examine the `comics` dataset

```{r}

```

## 2. Use `distinct` to find the different values of the `alive` variable

```{r}

```

- How many distinct values are there? 
  
- Are there any missing values?  

## 3. Use `distinct` to find the different values of the `publisher` variable

```{r}

```

- How many distinct values are there? 

- Are there any missing values?  


## 4. Create a new object `df_comics` 

- Filter out any missing values for `alive` and `publisher` 

- Select the `alive` and `publisher` variables

- Assign the output to `df_comics`

  
```{r}

```

# Use the `df_comics` dataset for the rest of the questions 

## 5. Create a contingency table of the variables `alive` and `publisher`

(Hint: look at the code for to create the contingency table for the variables `align` and `id` in the tutorial)


```{r}

```


* The count of the category with the most observations is________
  
* The value of `alive` is __________

* The value of `publisher` is __________

## 6. Create a bar chart with the variable `publisher` 

```{r}

```

## 7. Create a stacked bar chart with the variables `publisher` and `alive`  

* Split the `publisher` bars into the `alive` categories. (Hint: `alive` will be the fill variable)


```{r}

```

## 8. Create a side-by-side bar chart of `publisher` by `alive`

```{r}

```

## 9. Create a mosaic plot of `publisher` by `alive`

```{r}

```

* Do the publishers have approximately the same proportions of deceased characters? (yes, no, can't tell)
