---
title: "10 - Visualization"
execute: 
  warning: false
---



## Load libraries and data

```{r}
library(tidyverse)
library(scales)
library(skimr)
library(plotly)
theme_set(theme_minimal())
```

## Read the data in 

- [Pupil-teacher ratios](https://ourworldindata.org/teachers-and-professors#pupil-teacher-ratios-for-primary-education-by-country)

```{r}
pupil_teacher_ratio <-  read_csv("https://bus320-quarto.netlify.app/data/pupil-teacher-ratio-for-primary-education-by-country.csv")
```

## 1. `skim` the data

- Use `skim` to summarize the dataset

```{r}

```

* Which variable(s) have missing values?



## 2. Eliminate the missing values

- Eliminate the rows of `pupil_teacher_ratio` that have missing values

- Save the output to `pupil_teacher_ratio_no_missing`

- Display `pupil_teacher_ratio_no_missing`

```{r}

```


## 3. `skim` the `pupil_teacher_ratio_no_missing` data


```{r}

```

* What is the mean pupil-teacher ratio for the countries in `pupil_teacher_ratio_no_missing`? 

* What is the standard deviation of the pupil-teacher ratio for the countries in`pupil_teacher_ratio_no_missing`?

* What is the minimum pupil-teacher ratio for the countries in `pupil_teacher_ratio_no_missing`?

* What is the median pupil-teacher ratio for the countries in `pupil_teacher_ratio_no_missing`?

* What is the maximum pupil-teacher ratio for the countries in `pupil_teacher_ratio_no_missing`?

## 4. Count the number of observations for each `Entity` 

- In `pupil_teacher_ratio_no_missing`, count the number of observations for each `Entity`


```{r}

```

## 5. Randomly select 4 entities to analyze

- Use `set.seed()` so your results will be replicable.  Set your seed to the length of your first name in Moodle.  For example, if your first name is "Elizabeth", set your seed to 8. 
  
  - set.seed(8)

- Use `slice_sample()` to randomly select 4 entities from `pupil_teacher_ratio_no_missing` and save to `entities`

  
```{r}

```  

## 6. Display `entities`

```{r}

```


## 7. Format and select the data for plotting


- Extract only the rows for the 4 entities from `pupil_teacher_ratio_no_missing` 

- Rename the last column to `pupil_teacher_ratio`

- Drop the variable `Code`

- Save to object `pupil_teacher_df`


```{r}


```

## 8. Display `pupil_teacher_df`

```{r}

```

## 9. Compute the min and max Year

- Start with `pupil_teacher_df`

```{r}


```

* The minimum Year is: 

* The maximum Year is:

## 10. Plot `Year` vs `pupil_teacher_ratio` for each entity

- Use `ggplot2` to create a line plot for each entity with `Year` on the x-axis and `pupil_teacher_ratio` on the y-axis (hint: color = `Entity`)

- Add points to the plot

- Add a title, "Pupil-teacher ratio for primary education, min year to max year"

- Add subtitle, "Average number of pupils per teacher, based on headcounts of both pupils and teachers.
When feasible, the number of part-time teachers is converted to ‘full-time equivalent’
teachers; so that a double-shift teacher is counted twice, etc."

- Add a caption, "Source Our World in Data (https://ourworldindata.org/teachers-and-professors#pupil-teacher-ratios-for-primary-education-by-country)"

- Remove the x and y axis and color labels

- Save the plot to `p_pupil_teacher_df`

- Display `p_pupil_teacher_df`

```{r}


```

## 11. Make `p_pupil_teacher_df` interactive 

* Use `ggplotly`


```{r}


```

## 12. Add text the plot

- Add a text annotation to `p_pupil_teacher_df` that describes an interesting observation about the data

```{r}


```
